---
title: "HA - Buergerhaushalt"
author: "Anthea von Borowski"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Toulouse

## Step 0 : import libraries

```{r libs}

requiredpackages <- c('ggplot2', 'quanteda', 'quanteda.textstats', 'here', 'dplyr', 'stringr', 'wordcloud', 'deeplr', 'purrr', 'polyglotr', 'stm', 'tm', 'dendextend')

install_load <- function(packages){
     for (p in packages) {
          if (p %in% rownames(installed.packages())) {
               library(p, character.only=TRUE)
          } else {
               install.packages(p)
               library(p,character.only = TRUE)
          }
     }
}

install_load(requiredpackages)



if (!require("pacman")) install.packages("pacman")
pacman::p_load_current_gh("trinker/lemmar")


```

## Step 0 : Load the data

```{r load data}

bp_toulouse <- read.csv(here("data", "propositions-demarches-participatives-je-participe-toulouse.csv"), sep = ",")

bp_toulouse <- bp_toulouse %>%
  filter(nom_page_projets %in% c("bp2023", "mes-idees-pour-mon-quartier")) %>% 
  distinct(reference.contribution, .keep_all = TRUE)


bp_toulouse$année <- as.numeric(gsub("BP", "", bp_toulouse$année))

bp_toulouse$contenu <- gsub(
  "\\bb\\s*timent(s?)\\b",
  "batiment\\1",
  bp_toulouse$contenu
)

bp_toulouse$contenu <- gsub("\u00B2", "2", bp_toulouse$contenu)

bp_toulouse$contenu <- gsub(
  "^\\s*((Cette idée a été transmise via un formulaire papier par\\s+[^.]+\\.\\s*|Idée originale\\s+(publiée par|transmise via un formulaire papier|transmise via formulaire papier)\\s+[^:.]+[.:]?\\s*|L?'?\\s?ID[ÉE]E?\\s+EXPRIM[ÉE]E?\\s+PAR\\s+@?[^:]+:\\s*|//.*User/\\d+\\s*:?\\s*|:User/\\d+\\s*:?\\s*|//[^:]+:\\s*))+",
  "",
  bp_toulouse$contenu,
  perl = TRUE)

bp_toulouse$modalities <- sub(
  ".*?(Modalités de réalisation :.*)",
  "\\1",
  bp_toulouse$contenu
)


bp_toulouse$modalities <- ifelse(
  grepl("Modalités de réalisation\\s*:|CE QUE PRÉVOIENT LES SERVICES\\s*:",
        bp_toulouse$contenu,
        ignore.case = TRUE),
  sub("(?s).*?(Modalités de réalisation\\s*:|CE QUE PRÉVOIENT LES SERVICES\\s*:)\\s*",
      "",
      bp_toulouse$contenu,
      perl = TRUE),
  NA
)

bp_toulouse$contenu <- sub(
  "(?s)\\s*(Modalit[ée]s de r[ée]alisation\\s*:|CE QUE PR[ÉE]VOIENT LES SERVICES\\s*:).*",
  "",
  bp_toulouse$contenu,
  perl = TRUE
  )

bp_toulouse$contenu <- gsub("^\ufeff", "", bp_toulouse$contenu)



Unaccent <- function(text) {
  text <- gsub("['`^~\"]", " ", text)
  text <- iconv(text, to="ASCII//TRANSLIT//IGNORE")
  text <- gsub("['`^~\"]", "", text)
  return(text)
}

bp_toulouse$contenu <- Unaccent(bp_toulouse$contenu)
bp_toulouse$contenu <- gsub("\n", " ", bp_toulouse$contenu)

bp_toulouse$contenu_raw <- bp_toulouse$contenu

bp_toulouse$contenu <- gsub(
  "\\b[ldjscmuty] ?(\\?'|') ?",  # erfasst ' oder \' mit optionalem Leerzeichen davor/nach
  "",
  bp_toulouse$contenu,
  ignore.case = TRUE
)


```

## Step : create a corpus

```{r corpus}

toulouse.corpus <- corpus(bp_toulouse$contenu, 
                      docvars = data.frame(projectId =bp_toulouse$reference.contribution, category = bp_toulouse$catégorie, location = bp_toulouse$ref.territoire, title = bp_toulouse$titre, year = bp_toulouse$année, votes = bp_toulouse$vote, support = bp_toulouse$soutien, accepted = bp_toulouse$état) )

toulouse.corpus$year <- as.numeric(toulouse.corpus$year)
toulouse.corpus$date <- as.Date(toulouse.corpus$date)
toulouse.corpus$votes <- as.numeric(toulouse.corpus$votes)
toulouse.corpus$support <- as.numeric(toulouse.corpus$support)


```

## Step 2 : extract tokens

### Extract all tokens

```{r tokens-all, echo=FALSE}


toks <- tokens(toulouse.corpus,
               remove_punct = T, 
               remove_url = T,
               remove_symbols = T,
               )

toks <- tokens_remove(toks, stopwords("french"))


toks <- tokens_tolower(toks)
```

### Handle ngrams

```{r ngrams}

toks.ngrams <- tokens_ngrams(toks, n= 2:5)

## Normalizing tokens

# Find all ngrams starting with street type
ngram.locations <- tokens_select(toks.ngrams, pattern = "^(?:rue|avenue|boulevard|route|allee|allees|place|bd|pont|chateau|chemin|impasse)_(?!.*_(?:rue|chemin|impasse|bd|places|rues|avenue|chateau|boulevard|route|allee|voie|allees|place|quartier|pont)(?:_|$)).*", valuetype = "regex")


ngram.nonlocations <- tokens_remove(tokens_ngrams(toks, n = 2:3), pattern = "^(?:rue|avenue|boulevard|route|allee|allees|place|bd|pont|chateau|chemin)_(?!.*_(?:rue|chemin|bd|places|rues|avenue|chateau|boulevard|route|allee|voie|allees|place|quartier|pont)(?:_|$)).*", valuetype = "regex")

```

#### Define non-street words

```{r non-street 1}
non_street_words_1 <- c(
  "plus","peut","etre","donc","tres","faire", "depuis","notamment","entre",
  "vers", "propose","proposition","agreable", "creer", "ou", "etroite", "ainsi",
  "aussi", "comme", "etre", "puisse", "pourrait", "car", "n'est", "compliquee",
  "conduira", "jusqu'a", "proche", "empruntee", "continuer", "afin", "compris",
  "echangeurs", "exemple", "trottoir", "autres", "autre", "possede", "arriere",
  "secteur", "fluidifier", "sortir", "supprimer", "partie", "acces", "devant", 
  "derriere", "pratiquement", "objectif", "fois", "radar", "interdit", 
  "supprimant", "stationnement", "viens", "association", "retirer", 
  "frequentee", "velos", "cote", "cotes", "longe", "ligne", "trop", "eloignes", 
  "eloigne", "betons", "nombreux", "nombreuses", "recu", "revetement", 
  "plantes", "planter", "securite", "situee", "accessible", "ajouter", 
  "ameliorer", "ajouter", "faciliter", "securiser", "barrieres", "bancs", 
  "cameras", "certains", "consisterait", "devient", "fait", "puis", "quelque", 
  "quelques", "aujourd'hui", "entierement", "installee", "monument", "panneau", 
  "parking", "simplifier", "voitures", "pernettrait", "verdir", "publicites", 
  "repositionner", "panneau", "zones", "gagnee", "gestion", "composteur",
  "pistes", "angle", "installant", "interessant", "balader", "grandeur", 
  "suffisant", "existe", "empruntent", "outre", "montant", "tout", "favorisant",
  "devenue", "possibilite", "possible", "sens", "toilettes", "observera", 
  "eclairage", "detection", "meriterait", "empeche", "murs", "beaucoup", 
  "va", "rendre", "certaines", "axe", "permet", "traces", "traversee", "tables",
  "boite", "partage", "piste", "pouvoir", "remplacer", "parvis", "faudrait", 
  "a", "resultat", "separant", "arbres", "remedierait", "boulodrome", 
  "pietonne", "continuite", "producteurs", "doit", "raisons", "existante", 
  "genera", "goudronnee", "relativement", "font", "curieux", "mene", "niveau",
  "modes", "circulation", "traffic", "constitue", "toujours", "poussettes", 
  "reintroduction", "remonter", "reservee", "entrainent", "savourer", 
  "vegetalisee", "aimerions", "passent", "croisement", "tous", "effet", 
  "arrivent", "condamne", "aucune", "ralentisseurs", "rejoindre", "besoin", 
  "creant", "otes", "direction", "habitants", "deja", "extremement", 
  "dangereux", "particulierement", "betonnees", "cyclistes", "contre-allee", 
  "budget", "sait", "beneficient", "beneficier", "celle", "frequente",
  "remplacant", "recuperer", "penche", "trouve", "existant", "idee", "consiste",
  "installer", "remettre", "parfois", "insuffisantes", "garage","societe",
  "comporte", "terrain", "coupure","devenus", "memes", "passer", "si", 
  "probablement", "remplies", "reduire", "connaissent", "sejourne", "reserver",
  "contre", "velo", "regulierement", "bruyante", "pietons","polluee", 
  "dangereux", "dangereuse", "emplacement", "jusqu'au", "depourvue", "capacite",
  "isoler", "table", "choix", "mauvais", "etat", "trouve", "signe", "stop", 
  "donner", "31400", "montrent", "sortie", "est-il", "enjambant", "espace", 
  "encouragerait", "insuffisamment", "encourager", "vegetalisation", "peuvent", 
  "serait-il", "difference", "exposee", "faut", "pertinent", "plantant", 
  "demineraliser", "equiper", "fronton", "est-a", "toulouse", "camp", "contexte", 
  "entraine", "chaque", "continuation", "conteste", "pleines", "resonnent", 
  "manquent", "enrobes", "mettre", "scooter", "venues", "beneficient", 
  "conservant", "portion", "restent", "compromet", "respectent", "impliquera", 
  "pourquoi", "seule", "revaloriserait", "egalement", "tournant", "face", 
  "toulousain", "moins", "emettent", "emprunte", "entree", "equipee", 
  "etrangement", "prolongement", "proximite", "bordee", "limitation", "seceur", 
  "vu", "depart", "la", "cote", "replanter", "necessiterait", "veritables", 
  "insuffisante", "manque", "faisant", "circuler", "encombrees", "bitume", 
  "habitations", "relier", "cependant", "developpent", "limiterait", "rien", 
  "jamais", "lors", "n'en", "lorsque", "longee", "destruction", "impossible", 
  "surtout", "est-ce", "barre", "30_km_h", "concentre", "creation", "neanmoins",
  "inciter", "passant", "renovee", "reste", "dissuade", "encouragement", 
  "realiser", "n'a", "pente", "vehicules", "calibree", "pieton", "circulee", 
  "prix", "defaut", "projets", "reste", "sert", "recoit", "rarement", 
  "morphologie", "partir", "meritent", "souhaiterai", "suant", "creche", 
  "rectiligne", "indispensable", "convient", "contribuer", "vegetaliser", 
  "nuisances", "entrainant", "beneficie", "rend", "helas", "peu", "donne", 
  "coupes", "plutot", "bordure", "bord", "contenter", "parfait", "rajouter",
  "particulier", "occasion", "verifier", "represente", "quand", "elargissement", 
  "vraiment", "station", "barriere", "evitant", "bouchons", "embouchure", 
  "priorite", "idealement", "eviter", "synchrone", "mise", "frequemment", "raison", "liasse", "banalisation", "minutes", "lequel", "retrouvent", "severac.creer", "retrouvent", "celui", "plantation", "zone", "frequemment", "feu", "debouche", "laissent", "jouissance", "maintenant", "met", "nouvel", "pouvez", "presente", "separee", "ni", "offrirait", "impasse", "bande", "souhaitant", "interdiction", "cause", "proposons", "prolonger", "prejudiciable", "fasse", "lotissement", "embellissant", "gere", "garonne-creer", "laisse", "forcement", "devait", "beton", "bibliobus", "500", "blocs", "boites", "completement", "immense", "bornes", "recharge", "meriteraient", "cables","centaines", "camera", "bus", "drainer", "calme", "image", "marquage", "capteurs", "cendriers", "chemin", "boire", "chez", "choses", "circuit", "cloture", "coin", "collecteur", "complexe", "compost", "consequences", "prochainement", "vegetalisant", "cuisson", "cultiver", "defectueuse", "suggere", "degagee", "davantage", "demandent", "defibrillateur", "desertee", "devise", "heurtent", "disponible", "depasser", "rendant", "elargir", "emblematique", "dispositif", "dispositifs", "double", "due", "retrouvent", "encore", "endroits", "enlever", "eponyme", "equipements", "symetrie", "31300", "gagnerait", "vide", "embellie", "favoriser", "containers", "fruits", "legumes", "futurs", "gardant", "souvent", "cacher", "rajoutant", "gauche", "vis", "feu", "finalement", "fermeture", "garder", "role", "gaz", "endroit", "rond", "bougainvilles", "image", "immeuble", "pres", "30", "inversement", "49", "participer", "transverse", "pleine", "trajet", "couloir", "12", "interruptions", "laisse", "lieu", "couper", "bloquent", "rocade", "matabiau-canal", "rehabiliter", "bourassol-patte", "voit", "ressemble", "rive", "1860", "cultivant", "bacs", "enlevant", "perpendiculaires", "complement", "brumisateurs", "ceux", "chicanes", "clapets", "mieux", "collecte", "partenariat", "cours", "creent", "cuisiner", "demarches", "distributeur", "installations", "habitation", "handicapee", "gymnase", "implanter", "bouganvilles", "infrastructures", "insonoriser", "initiative", "integrant", "interdire", "installations", "interet", "entoure", "fournirait", "jeux", "acces", "duree", "bourrassol-patte", "pourra","energies", "give", "intercalant", "infrasctructures", "comprend", "perimetre", "objet", "supermarche", "journees", "liberee", "lutter", "livraison", "m113a", "maisons", "malheureusement", "maniere", "provisoirement", "provoque", "provenance", "proprete", "projet", "privees", "presence", "preferentielle", "preferable", "environ", "pourrions", "retrouve", "poussette", "plots", "plantee", "remplaces", "compte", "ehpad", "circulant", "fast-foood", "refaites", "systematiquement", "goudron", "reflechissons", "reduction", "trait", "venant", "reamenageant", "dispose", "realisant", "re-amenagee", "redefinir", "orientation", "rappels", "quid", "quotidiennement", "raphaa", "quartier", "traverse", "devra", "battu", "coherence", "pieges", "centre-ville", "navette", "navettes", "marne-av", "habitent", "poteaux", "mesure", "mesures", "minibus", "mobilites", "moyens", "operations", "cumulent", "fermant", "nuit", "nouveaux", "pris", "organisation", "prendre", "rechauffement", "saint-cyprien.aujourd_hui", "voient", "parcelle", "fonctionne", "dedie", "depourvu", "epanouiront", "reseaux", " coulee", "etroit", "etroits", "43.598943647677885_1.3764622769253738", "sequences", "remarque", "solutionnerai", "inutilisiable", "piteux", "cinquantaine", "hangas", "mal", "retour", "friche", "pedestre", "prive", "31100", "devenu", "conducteurs", "joli", "oblige", "multiplication", "uniquement", "debitumant", "pk", "devienne", "favorables", "rappel", "organisant", "redevenu", "strictement", "ponsan.il", "directement")

```

```{r non-street 2}

non_street_words_2 <- c("dessert", "constituee", "peri", "penaliser", "pendant", "propre", "gratuit", "pate", "souffre", "partagent", "brumisateur", "prenant", "compte", "oubliee", "hors", "obstacle", "oppose", "numeros", "non", "nommee", "relie", "nettoyage", "nature", "emprunter", "delimite", "mobile", "constatons", "minuscule", "voisins", "michl", "merite", "merci", "31200", "segment", "sous", "vegetaliser", "malgre", "meilleurs", "maison", "residents", "velo", "vegetalise", "vegetal", "utilisee", "trier", "tres", "stade", "type", "difficultes", "train", "surchargee", "necessaire", "deplacements", "revienne", "souhaite", "vegetation", "semblent", "durant", "scolaire", "securisant", "securisee", "inadapte", "reparation", "intersection", "chaussee", "etc", "enterrer", "reverdir", "option", "retrouvee", "residentielles", "reprise", "largeur", "contournable", "147", "desservir", "limite", "limiter", "bcp", "descente", "70m", "baignee", "installation", "mis", "investie", "implantation", "inexistants", "hyper", "horaires", "remontant", "ilots", "partant", "clinique", "esperant", "imp", "irriguant", "95", "emprise", "gamelin.je", "decalant", "ressortir", "difficilement", "fermee", "jonction", "renforce", "parklets", "facon", "depend", "exposition", "etrique", "etendre", "etroite", "eventuellement", "desormais", "enfants", "enfouissement", "enfin", "creer", "elargir", "31500", "construction", "tres", "noa", "troncon", "dont", "tant", "descente", "montee", "des7", "deplacer", "deploiement", "depense", "densite", "invivable", "supression", "reliant", "chaussee", "parallele", "pratique", "changer", "90", "concevoir", "135", "telle", "rejoignent", "semi-pieton", "collecte", "desagrement", "envahies", "ouvert", "rejoint", "detecteur", "supplementaire", "offre", "prevues", "minimes", "ecluse", "clairement", "beneficiait", "benefice", "pourtant", "principaux", "cout", "rappeler", "verrai", "utilise", "composee", "tramway", "transition", "trous", "sorte", "restituer", "plan", "passe", "penser", "parle", "occuper", "note", "menant", "virage", "identifier", "usagers", "ðÿš", "inutile", "implique", "impraticable", "habitons", "gener", "incivilites", "expliquons", "encercle", "baptisee", "contraignant", "continue", "difficile", "contourner", "n'y", "completement", "comite", "but", "bouchent", "ponctuee", "inferieure", "constante", "limitee", "jusqu", "conformes", "vitesse", "ferree", "virage", "vielles", "tramway", "stadium", "tentes", "resoudrait", "maintenir", "veritable", "offre", "cede", "parallele", "3m", "indique", "menant", "m916", "limite", "necessite", "ferme", "garantir", "facon", "etouffante", "equipes", "enjambe", "echangeur", "dessus", "denue", "desaffecte", "revoir", "n'y", "coupe", "capture", "bout", "debroussailler", "pierre.sur", "semble-t-il", "coupe", "conviennent", "considerable", "reliant", "genre", "prevoir", "delimitation", "cree", "3,5", "continue", "partage", "inconfortable", "encombre", "800m", "cyclable", "vivent", "vivante", "video", "verte", "venir", "usagers", "uritrottoirs", "tri", "tonnelles", "telle", "terrasses", "federateurs", "systemes", "systeme", "substrat", "stocker", "stands", "tarif", "constamment", "service", "solutions", "reellement", "sortes", "securisation", "serait-elle", "week-end", "parcourt", "hasardeuse", "connecte", "via", "faudra", "fctn", "egards", "suppression", "termine", "inverser", "cout", "voir", "ferait", "trace", "semble", "cyprien.aujourd'hui", "envisage", "repondrait", "reduirait", "religion", "redevienne", "recuperateurs", "recuperation", "redonner", "recemment", "ralentisseur", "rapidement", "rafraichir", "quasi", "qu'un", "qu'elle", "qu'avant", "produire", "prises", "processus", "programme", "poser", "potelets", "moches", "poubelles", "immonde", "mesurable", "elle-meme", "pilonnes", "partout", "perdue", "parcours", "residence", "n049", "recoit", "integrer", "rampe", "securise", "etait", "demandais", "demeure", "meme", "elargissant", "enfoussiment", "ete", "respectee", "lourdement", "mac", "debitumiser", "etant", "bonjour", "remplacant", "ombrieres", "re-qualifier")

```

```{r concat non-street}
non_street_words <- c(non_street_words_1,non_street_words_2)
```

#### Define ending non-street words

```{r ending-non-street}
ending_non_street1 <- "|sens|petit_palais_sports_travaux|4|groupe|equipe|halage_berges_garonne|halage_berges|halage|marche_bio_1_jour|desa|local|vigne|innocent|tunnel|fil_eau|fil|marche_bio_1|fer|marche_bio|marche|marche_cochons_jour_meme|marche_cochons_jour|marche|petit_palais_sports|petit_palais|pradettes_square_camille_poinas|15|passage_sureleve|passage|petit_rucher|petit|patte_oie_ca|patte_oie|patte|petits|pinel_parc_qu'elle|place_surface|place|pinel_parc|pradettes_square_camille|pinel_ecole_cercle_laa|pinel_ecole_cercle|pinel_ecole|plein_soleil|plein|pradettes_square|soir_semaine_persuadee|soir_semaine|soir|concorde_bld_matabiau|vraie|grace|meilleure|placette|premiere|catalans_ponts_jumeaux|catalans_ponts|michel_berges_garonne|neuf_melange|michel_berges|bonnat_lien_ecole|bonnat_lien|concorde_bldcugnaux_ecole_patte_oie|cugnaux_ecole_patte|cugnaux_ecole|cugnaux_ecole_patte|cugnaux_ecole|ecole_maternelle|ecole|camboulives_ville|bas|pied|lardenne_point_strategique|lardenne_point|wilson_samedi|cyprien_capitole_st|cyprien_capitole|temps|vieux_centre_pied_vieux|vieux_centre_pied|vieux_centre|vieux|square_charles_gaulle|square_charles|demoiselles_canal|bearnais_canal_midi|bearnais_canal|stadium|bel|minimes_eglise_minimes|demoiselles_saouzelong_st|demoiselles_saouzelong|demoiselles_royaume|demoiselles_ormeaux|garonne_praticable_pied|garonne_praticable|minimes_eglise|voie|beau|neuf_quais_daurade|neuf_quais|rose_ville_rosea|rose_ville|nord_ile|bien_qu'il_strictement|bien_qu'il|bien|blagnac_college_ecole|voie_ferree_st|voie_ferree|voie|blagnac_college|voisin_montaudran|voisin|bayonne_saint_martin_touch|bayonne_saint_martin|bayonne_saint|meilleur|espagne_saint_cyprien_marche|espagne_saint_cyprien|espagne_saint|enfants|espagne_seysse_muret|espagne_deux_engagement_jean|espagne_deux_engagement|espagne_deux|espagne_seysse|morisot_enfants_marchent|ville|urgent|mediatheque|morisot_enfants|petit_parcours|petit|casernes_bien_qu'il|casernes_bien|notable|castanet_roseaux_pivoines_pelude|castanet_roseaux_pivoines|castanet_roseaux|cugnaux_nungesser_coli|belle|petites|cugnaux_nungesser|ecoles_fermee|petites|delherm_fer_cheval_engorge|delherm_fer_cheval|delherm_fer|ecoles|gibert_deux_residences_recentes|former_large_ecran|former_large|former|gambetta_quai|fondeville_ecole_nd|fondeville_ecole|gambetta_quai_daurade|gibert_deux_residences|gibert_deuxlongueur|bergson_ecole|grand_vent_bougent|grand_vent|grand|lemercier_ensemble|liaison_douce|jardins_fond_rares_petits|jardins_fond_rares|jardins_fond|liaison|grands|cel|juste|deux|bon|promenade|passage|deux_beaux|grand|grand_transformateur|vrai|cote|coup|tete|deux_voies|long_garonne|garee_sncf_saint|hauts_lieux_culture|grand|deux_bacs|point|grand_jet_eau_visible|zac_mairie|grand_parc_enfants|hortensias|places_parcs|places|urbain_canal_st-martory_bucsm|urbain_canal_st-martory|urbain_canal|urbain|2_jours_semaine_soir|2_jours_semaine|2_jours|4_oui_oui_voies|4_oui_oui|4_oui|4|portes_centre-ville|nouveau_integralite|nouveau|moment_morts|moment|bien_troue|grande_vigne_derniere|grande_vigne|ex|garde|chateau_hers|chateau|complique|fer_bibliotheque|fer_peinture|hangars_poudrerie|itineraire|haut|mur_briques|mur|chaleur|bld"

ending_non_street2 <- "a_formation_equipes|a_formation|a|4_references_velobs_dont|4_references_velobs|4_references|gare_sncf_saint|gare_sncf|gare|ecole|boulangerie|hauts_lieux|hauts|rolland_garros_ensemble|cafe|gloire_jardin|grande-bretagne_jardin_barry|grande-bretagne_jardin|parc|20_gare_matabiau|20_gare|20|section|riquet_fort_impact_qualite|riquet_fort_impact|riquet_fort|estrapade_port_viguerie_garonne|estrapade_port_viguerie|estrapade_port|job_jardin_ludotheque_disparues|job_jardin_ludotheque|job_jardin|jolimont_mediatheque_interessant|jolimont_mediatheque|lafourcade_gare_saint|lafourcade_gare|mairie_fleurs_mur|mairie_fleurs|mairie|poids_huile_temps|poids_huile|souffrent|poids_huile_conflits|places_pmr|places|providence_ecole_danse|providence_ecole|place|petite|periole_parc_observatoire|periole_parc|parcs|1_personne|1|grandes|maryse_bastie_ecole_maternelle|maryse_bastie_ecole|marguerite_duras_salle_polyvalente|marguerite_duras_salle|marcel_bouvier_jardins|balansa_lyceens_externes|balansa_lyceens|temps|veillon_premier_temps_ilot|veillon_premier_temps|veillon_premier|st_ursulle_prieure|saint|st|rues|prise|iv_large_14|iv_large|plana_bien_qu'il|plana_bienvilleneuve_bonjour|roquelaine_droite_longue_407|roquelaine_droite_longue|roquelaine_droite|villemur_point_nevralgique|villemur_point|2|voies|vie_enfants_enterrer_reseau|vie_enfants_enterrer|vie_enfants|sports_college_ecole_maternelle|voie_ferree|voie|rue_raymond_iv|rue_raymond|rue|heures|nord|sud|est|ouest|rares|semi|sports_college_ecole|sports_college|petite|horloge|seul|seuls|square|st_michel_milieu|street_basket_graph_street|street_basket_graph|street_basket|street|st_michel_soumise|manufacture|2_4_roues|2_4|2|bien|planet|principale|voie_issue|issue|longues|grande|route|rond|p|long_voie|long|2_voies|petit_detour_300m|matins_soirs|cite|passages_etroits|passages|petit|long|large|tete_beche|tete|portes|petit_detour|matins|portes_entree|portes|larges|triangle_laisse|trianglr|jacques_chirac_or|triangle|nouveau|voie|longue|2_3_bacs|2_3|grande_grande_bretagne|grande_grande|grande|castres_muret|deodat_lycee|bis|jet_eau|jet|journee|journee_retirant|flux_doux|doux|groupes_parole|groupes|ecole_primaire|job_ecole|jour|marche_grand|marche_grand_mur|marche_plein_vent_samedi|marche_plein_vent|marche_plein|bas_digue|bas|caillibens_unique_moyen|caillibens_unique"

ending_non_street <- paste0(ending_non_street1, ending_non_street2, sep = "|")

```

#### Remove tokens that contain undesired combinations

```{r cleaning ngrams}
repeat{
  
  

  ngram.locations <- tokens_remove(
    ngram.locations,
    pattern = paste0("_(?:", paste(non_street_words, collapse="|"), 
                     ending_non_street , ")$"),
    valuetype = "regex"
  )
  
  ngram.locations <- tokens_remove(
    ngram.locations,
    pattern = paste0("_(?:", paste(non_street_words, collapse="|"), ")"),
    valuetype = "regex"
  )


  if (length(table(as.character(ngram.locations))) == length(table(as.character(ngram.locations)))) break
}
  




# Remove sub-tokens
x <- types(ngram.locations)

remove_prefix <- sapply(x, function(i) {
  any(startsWith(x, paste0(i, "_")))
})

keep <- x[!remove_prefix]

ngram.locations <- tokens_select(
  ngram.locations,
  pattern = keep
)
```

#### Compound all tokens

```{r}


freq.ngrams.locations <- as.data.frame(table(as.character(ngram.locations)))
freq.ngrams.nonlocations <- as.data.frame(table(as.character(ngram.nonlocations)))

ngram.locations.insert <- gsub("_", " ", 
                               as.character(
                                 freq.ngrams.locations[order(
                                   -freq.ngrams.locations$Freq),]$Var1))
ngram.nonlocations.insert <- gsub("_", " ", 
                            as.character(
                              freq.ngrams.nonlocations[order(
                                -freq.ngrams.nonlocations$Freq),][1:100,]$Var1))


toulouse.compound.tokens <- tokens_compound(toks, phrase(ngram.nonlocations.insert), concatenator =  "_", join = F)
toulouse.compound.tokens <- tokens_compound(toulouse.compound.tokens, phrase(ngram.locations.insert), concatenator =  "_", join = F)
```

```{r }
# lemmatise each word ONCE
lemma_lookup <- setNames(lemmatize_fr(unique(tolower(unlist(as.list(toks))))), unique(tolower(unlist(as.list(toks)))))

# replace tokens via lookup
lemmatised_list <- lapply(as.list(toks), function(x) {
  lemma_lookup[tolower(x)]
})

lemma.toks <- tokens(lemmatised_list)







toulouse.tokens <- tokens_select(tokens(lemmatised_list), pattern = "^[0-9]+(\\.[0-9]+)?$", selection = "remove", valuetype = "regex")










```

## Step 3 : create a DTM and calculate TF-IDF

```{r tf-idf}

toulouse.DTM <- dfm(toulouse.tokens)

toulouse.dfm.tfidf <- dfm_tfidf(toulouse.DTM)

toulouse.dfm.tfidf

```

## Step 4 : compute LL for accepted = T / F

### Compute IDF

```{r}

toulouse.N.docs <- nrow(toulouse.DTM)
toulouse.ni.doc <- colSums(as.matrix(toulouse.DTM))
toulouse.idf <- log2(toulouse.N.docs / toulouse.ni.doc)

head(toulouse.idf)
```

### Compute TF-DIF for accepted == T

```{r tf-idf accepted}

dt.accepted <- which(bp_toulouse$état == T,)
toulouse.tf.accepted <- as.vector(colSums(toulouse.DTM[dt.accepted, ]))
names(toulouse.tf.accepted) <- colnames(toulouse.DTM)

toulouse.tf_idf.accepted <- toulouse.tf.accepted * toulouse.idf
names(toulouse.tf_idf.accepted) <- colnames(toulouse.DTM)

sort(toulouse.tf_idf.accepted, decreasing = T)[1:12]



```

### Compute TF-DIF for accepted == F

```{r tf-idf not accepted}

dt.not_accepted <- which(bp_toulouse$état == F,)
toulouse.tf.not_accepted <- as.vector(colSums(toulouse.DTM[dt.not_accepted, ]))
names(toulouse.tf.not_accepted) <- colnames(toulouse.DTM)

toulouse.tf_idf.not_accepted <- toulouse.tf.not_accepted * toulouse.idf
sort(toulouse.tf_idf.not_accepted, decreasing = T)[1:50]

```

### Compute the LL

```{r log-likelihood}

toulouse.a <- toulouse.tf.accepted#[toulouse.tf.accepted > 0]
toulouse.b <- toulouse.tf.not_accepted[names(toulouse.tf.accepted)]
toulouse.c <- sum(toulouse.tf.accepted)
toulouse.d <- sum(toulouse.tf.not_accepted)

toulouse.Expected1 <- toulouse.c * (toulouse.a+toulouse.b) / (toulouse.c+toulouse.d)
toulouse.Expected2 <- toulouse.d * (toulouse.a+toulouse.b) / (toulouse.c+toulouse.d)
toulouse.t1 <- toulouse.a * log((toulouse.a/toulouse.Expected1))
toulouse.t2 <- toulouse.b * log((toulouse.b/toulouse.Expected2))

toulouse.logLikelihood <- 2 * (toulouse.t1 + toulouse.t2)
length(toulouse.logLikelihood)

head(toulouse.logLikelihood)

```

### Identify over / underusage

```{r over/underusage}

toulouse.relA <- toulouse.a / toulouse.c
toulouse.relB <- toulouse.b / toulouse.d

toulouse.logLikelihood[toulouse.relA < toulouse.relB] <- toulouse.logLikelihood[toulouse.relA < toulouse.relB] * -1

sort(toulouse.logLikelihood, decreasing = T)[1:24]

sort(toulouse.logLikelihood, decreasing = F)[1:24]



```

```{r}


toulouse.top50 <- sort(toulouse.logLikelihood, decreasing = T)[1:50]
wordcloud(names(toulouse.top50), toulouse.top50, max.words = 50, scale = c(1, 0.8), colors = brewer.pal(8, "Dark2"), random.order = F)

```

## Step 5: Replace street names in the raw text

```{r define streets-additional}

freq.ngrams.locations <- as.data.frame(table(as.character(ngram.locations)))


additional_locations1 <- c("allees_paul_sabatier", "impasse_tocqueville", "place_lafourcade", "bd_lazare_carnot", "impasse_liliane_desgraves", "rues_st_joseph_dumeril", "place_busca", "faubourg_bonnefoy", "port-st-sauveur", "ponts_jumeaux", "av.g. pompidou", "place_heracles", "quai_daurade", "pont_blagnac", "place_ormeau", "rue_metz", "parc_marcaissonne", "boulevard_silvio_trentin", "rue_lafayette", "rue_lapeyrouse", "rue_arcs", "rue_cugnaux", "rue_carlos_gardel", "rue_louis_plana", "rue_metz", "rue_languedoc", "rue_isere", "av_de_muret", "rue_michel_ange", "rue_ausone", "route_launaguet", "pont_saint-sauver", "pont_montaudran", "rue_adonis", "chemin_lapparou", "avenue_minimes", "chemin_malepere", "chemin_carmes", "route_labege", "chemin_lapujade", "rue_antonio_vivaldi_gilles_goislard_monsabert", "rue_jean_arlaud", "rue_roger_arnaud", "marche_du_cristal", "rue_aubuisson", "avenue_lavaur", "boulevards_marquette_embouchure", "blvd_marquette", "blvd_lacrosses", "chateau_busca", "route_espagne", "chemin_lanusse", "bld_florence_arthaud", "rue_raymond_4", "rue_bayard", "rue_concorde", "allee_barcelone", "bd_lascrosses", "bd_armand_duportal", "rues_lancefoc_lejeune", "quartier_cartoucherie", "rue_fontaines", "rue_lambic", "avenue_lauragais", "barriere_paris", "rue_periole", "quai_oc", "placette_julie_jeanne_bouillane", "quartier_arnaud-bernard", "jardin_verrier", "quartier_bourrassol", "quartier_bonnefoy", "quartier_minimes", "rue_docteur_calmette", "rues_metz_boulbonne_croix-baragnon", "rue_achille_viadieu", "rue_anne_frank", "quartier_chalets-roquelaine", "roquelaine_concorde", "rue_simone_henry", "place_arago", "bourrassol-casselardit", "place_capitole", "rue_poids_huile", "square_charles_gaulle", "quartier_chalets", "rues_lancefoc_lejeune", "rue_alsace_lorraine", "rues_metz_boulbonne_croix-baragnon", "quartier_fontaine_lestang", "quartier_ballh", "quartier_belfort", "axe_denfert_rochereau", "quartier_patte_oie", "theuriet_galabert_gembloux_praviel", "quartier_bagatelle", "rue_artistes", "parc_niel", "eglise_saint_vincent", "parc_biscotte", "rue_valade", "place_anatole_france", "cloitre_chartreux", "chemin_sang_serp", "rue_emile_cartailhac", "quartuer_borderouge", "boulevard_arcole", "jardin_barry", "quartier_saint-agne", "rue_assalit", "avenue_urss", "rue_cheminots", "rue_saint- Laurent", "rue_armagnac", "rue_arago", "st-sernin", "rues_raspail_vitet_joseph_tillet", "avenue_atlanta", "quartier_montaudran_aerospace", "rue_adrienne_bolland", "rue_mal_clavel", "ch._bessemer", "ch_s._serp", "rue_amidonniers", "rues_taur", "rues_maurice_fort_plaisance_edmond_planet_chateaubriand_duploye", "rues_villet_cosmonautes", "periole_marengo_roseraie", "rue_varsovie", "quartier_guillaumet", "rue_alger", "rue_arnaud_baric", "parc_raymond_vi", "quartier_croix_daurade", "rue_lascrosses", "quartier_sept_demoers", "rues_saint-jean_pharaon_languedoc_ozenne", "rues_polinaires_languedoc", "rues_auguste_renoir_andre_vasseur_jean_seguy_colonel_remy","chemin_nicol",  "avenue_atlanta", "rues_tourneurs", "place_salin", "place_carmes", "st_simon_basso_cambo", "place_parlements", "place_auguste_albert", "sauzelong", "saint-cyprien", "place_antonin_froidure", "place_arnaud_bernard", "place_parlement_all_guesde", "place_niki_st_phalle", "place_amat_massot", "place_saint_pierre_daurade", "jardin_amour", "place_trinite", "parc_cedres", "place_st_aubin", "parc_cazal", "place_saint_caprais_cabarette", "place_andre_daste", "place_traces", "place_grimaud", "place_saint_pierre", "parc_bagatelle", "quartier_marengo", "place_agapito_nadal", "place_ahmed_chenane", "place_male", "pl._parlement", "place_aeropostale_montaudran", "pl._dupuy_st-aub", "bd_minimes", "lucie_aubrac", "jules_ferry", "avenue_albert_bedouce", "avenue_a_bedouce", "avenue_fronton", "avenue_etats_unis", "avenue_alain_gerbault", "canal_st-martory", "boulevard_embouchure", "canal_midi", "boulevard_lascrosses", "boulevard_gare", "boulevard_armand_duportal", "lardenne_sain_martin_blagnac")


additional_locations2 <- c("rues_languedoc_ozenne", "boulevard_cretes", "boulevard_atlanta", "place_carre_marengo", "guilhermy", "boulevard_j_chirac", "place_jolimont_mediatheque", "place_saint_aubin", "saint_aubin", "place_parfait_dalquier", "place_occitane", "place_curvale", "quartier_busca", "chemin_coin_moure", "avenues_camille_pujol_gloire", "jean_chaubet", "rues_bonnat_eugene_sue", "cours_dillon", "rues_cugnaux_arcs_saint_cyprien", "avenue_coteaux", "pech_david", "rue_avranches", "chemin_canal", "rue_vanini", "av_bedouce", "av_lauragais", "rue_perisse", "quartier_st_cyprien", "quartier_croix_daurade", "rues_david_elbaz", "chemin_argoulets", "boulevard_minimes", "quartier_lafourguette", "avenue_president_doumergue", "quartier_roseraie", "place_estrapade", "capitole_st_georges_trinite", "square_mady_laa_giraudiere", "rue_desa_amidonniers", "parc_niel", "rue_alexandre_faugiere", "rue_alsace", "rue_gallois_achille_viadieu", "rangueil", "st_agne", "rue_planet", "jardin_monplaisir", "avenues_crampel_saint-exupery", "rues_amiral_galache_san_subra", "rues_paix", "a._molles", "d._casanova_auber_toul", "rues_metz_croix-baragnon", "rues_languedoc_ozenne", "rue_alain_fournier", "rues_sainte_ursule_bourse_clemence_isaure_cujas_prieure", "rue_malbec", "rue_avranches", "rue_auch", "jardin_raymond_vi", "quartiers_bagatelle-faourette", "croix-daruade", "rue_arago_saint-louis", "rue_anges", "route_albi", "rue_simone_boudet", "quartier_cote_pavee", "chemin_chateau_hers", "rue_nicolas_poussin", "rue_abel_autofage", "place_patte_oie", "quartier_st-aubin_bedford_gabriel_perry", "quartier_st_aubin", "charles_fitte", "rue_plantier", "boulevard_carnot", "rue_adolphe_call", "av_crampel", "av_victor_segoffin", "square_herakles", "rues_chant_merle_pierre_larousse", "parc_violette", "eglise_saint-aubin", "rues_gonin_vedrines", "rue_nimes", "quartier_rangueil", "rue_caroline_aigle", "avenue_latecoere", "rue_adolphe_coll", "rue_alfred_vigny", "rue_val_aran", "rue_van_dyck", "saint-cyprien_saint-sernin", "rue_allier", "quartier_saint_etienne_carmes", "rue_arnaud_bernard", "quartier_soupetard", "route_agde", "parc_union", "rue_vasseur", "rues_regnault_ste_genevieve_aboukir", "avenues_jean_rieux_camille_pujol", "mozart_d_auch_turres_vestrepain", "rues_aspe_deffes", "bld_gle_eisenhower", "rues_domremy", "pont_stadium", "rue_paul_pujos_joubert", "rue_edmond_planet", "quartier_fontaine-lestang", "rue_aigle", "rue_vestrepain", "rue_ella_maillart", "jardin_yves_bergougnan-", "jardin_yves_bergougnan", "quartier_guilhermy", "route_st_simon", "cite_amouroux", "rues_vitet_pradal_noulet", "rues_gauthier_gilbert_getten", "chemin_lafilaire", "rues_entre_sain-sernin_arnaud_bernard", "boulevard_minimes", "rue_abbe_sicard", "rue_ourq", "quartier_brouardelle/europe", "av_st_exupery_ou_jean_rieux", "rues_antonio_vivaldi_gilles_goislard_monsabert", "quartier_saint-aubin", "ile_ramier", "quartier_lafourguette", "avenue_lamartine", "av_aerodrome_montaudran", "av_lyon", "fbg_bonnefoy", "quartier_st-cyprien", "av_jean_jaures-", "bd_gare", "av_lardenne", "av_arenes_romaines", "av_aerodome_montaudran", "av_urss", "av_a._bedouce", "quartier_saouzelong", "av_larrieux", "av_casselardit", "av_lombez", "av._URSS", "av._14eme_regiment_infanterie", "av._coteaux", "av._fronton", "place_roger_arnaud", "av._jean_rieux", "place_armand_leygue", "av._ducuing_salade_ponsan", "latecoere_aerodrome_herbettes_struxianola", "av._ducuin_salade_ponsan", "av._de_casselardit", "av._honore_serres", "av._lespinet", "bd_deodat", "boulevard_deodat", "bd_silvio_trentin", "bd_arcole", "quartier_st-cyprien", "bld_deodat", "bld_griffoul_dorval", "avenue_larrieu", "parc_gironis", "avenue_fronton", "pont_minimes", "eglise_minimes",  "avenue_lardenne", "avenue_lattre_tassigny", "avenue_etats-unis",  "cimetiere_terre_cabade", "ormeau-deltour", "avenue_aristide_briand", "avenue_louis_plana", "quartier_saint_cyprien", "garonne")

additional_locations3 <- c("bd_minimes", "avenue_avions", "avenue_c._flammarion", "jardin_observatoire", "avenue_arenes_romaines", "saint_martin_touch", "parc_merlettes", "parc_boiseraie", "parc_francois_longaud", "parc_maourine", "parc_saisons", "square_mady_giraudiere", "quartiers_bazacle_amidonniers", "esplanade_montaigut", "parc_fontaine_lestang", "jean_pierre_vernant_pouvourville", "parc_bourrassol", "parc_fouerette", "quartier_saint_michel", "parc_poudrerie", "parc_compans_caffarelli_prairie_filtres", "zac_saint_exupery", "parc_barry", "parc_farouette", "parc_alalouf", "parc_7_deniers", "parc_raymond_6", "parc_roquemaurel", "parc_observatoire_jolimont", "parc_petit_bois", "rue_caravelle", "parc_observatoire", "parc_viollet_duc_pradettes", "parc_ramier", "quartier_croix_pierre", "parc_boiseraie", "parc_flambelle", "parc_arenes_romaines", "parc_perry", "port_embouchure", "parc_pouvillon_parc_fontaines", "parc_vestrepain", "parc_louis_vestrepain", "foyer_etienne_billiere", "parc_telegraphe", "parc_pouvillon", "parc_gironde", "parc_saccarin", "parc_couserans", "parc_ritouret", "parc_argoulets", "parc_maurice_becanne", "parc_nougaro", "parc_sept-deniers", "parc_fontaine-lestang", "parc_petit_prince", "parc_gounon",  "parc_compans-caffarelli", "parc_allalouf", "parc_ducis", "quartiers_ancely_casselardit", "grand_parc_garonne", "parc_abattoirs", "parc_sept_deniers", "quartier_bellefontaine", "parc_clairfont", "parc_ramiers_blagnac", "parc_sacre_coeur", "parc_compans", "parc_boisseraie", "verstrepain_fontaine_lestang_biscottes", "parc_touch_canal", "jardin_royal_plantes_compans", "bayard_matabiau", "barigoude", "dortis_josephine_baker", "anthonioz_gaulle", "cepiere_cartoucherie", "quartier_ginestous", "quartier_saint-sernin", "quartier_arenes", "quartier_arnaud_bernard", "axe_bourges_maunoury_netwiller", "quartier_hers", "quartier_saint-simon", "quartier_reynerie", "quartier_negreneys-minimes", "quartier_ancely", "quartier_achiary", "quartier_limayrac", "quartier_arenes_romaines_purpan", "quartier_saint_simon", "quartier_la_vache", "quartier_sept_deniers", "quartier_saint_etienne", "periole_marengo_roseraie", "quartier_guilhemery", "quartier_jeanne-d_arc", "quartier_licard", "quartier_st-michel", "quartier_matabiau", "quartier_jeanne_arc_belfort_bayard_jusqu_chalets", "quartier_jeanne_arc","quartier_jeanne_arc_matabiau", "quartier_3_cocus", "ch_izards", "quartier_empalot", "quartier_denfert_rochereau", "quartier_launaguet", "quartiers_chateau_hers","quartiers_saint-michel_empalot", "3_quartiers_chalets_compans_arnaud_bernard", "quartier_saint_cyp", "quartier_basso_cambo", "quartiers_casselardit-bourrassol", "quartiers_negreneys_minimes", "quartier_malepere_marcaissone_carmes", "quartiers_saint_agne_empalot", "quartier_ramassiers", "quartier_malepere_carmes", "quartier_toulouse_aerospace", "quartier_chemin_butte", "quartier_de_gloire", "quartiers_casselardit", "quartier_moscou", "stade_sergent_vigne", "esplanade_metro_vache", "quartier_compans", "quartiers_st-michel", "quartier_7-deniers", "quartier_lespinet", "quartier_bas_guilhemery", "quartier_raisin", "quartier_purpan", "quartier_amouroux", "quartier_papus", "quartier_casselardit", "ex_prison_saint_michel_villa_gabes", "ex_prison_saint_michel_barbacane", "moulins_poudrerie_villa_gabes", "quartier_ginestou", "quartier_pint_demoiselles", "quartier_iliade_ivry", "quartiers_guilhemery", "quartier_vauquelin", "quartiers_bafapatabor", "bagatelle_faourette_papus_tabar_bordelongue", "quartier_compans_caffarelli", "3_quartiers_amouroux_roseraie_reservoir", "quartiers_bagatelle_faourette", "quartiers_trois_cocus", "quartier_malepere_marcaissone", "quartier_saint-martin-du-touch", "quartier_jeanne_arc_jean_jaures", "quartier_colombette", "quartier_pointe", "tremie_saint_agne_pont_voie_ferree", "quartier_gramont", "quartier_malepere", "quartier_7_deniers", "pl_bories", "pl_arago", "pl_betaille", "pl_bartoli", "quartier_tibaous", "quartier_dortis", "quartier_papus", "quartier_bas_saint-michel", "quartier_st_simon", "quartier_st-simon", "quartier_lombez", "quartier_fondeyre")

additional_locations4<-c("bourrassol_casselardit", "marengo_bonnefoy", "petit_gragnague", "croix_daurade", "ste_germaine", "jean-pierre_vernant_pouvourville", "jules_julien", "jp_vernant_ch_pouvourville", "sainte_therese", "victor_hugo", "roualt_imp._francois_foulquier", "cote_pavee", "alphand", "grand_selve", "residence_gounon", "oustalous", "maourine", "jolimont", "patte_oie", "paul_bert", "nd_anges", "amidonniers", "ponts_minimes_matabiau", "chalets_st-hilaire_matabiau_bayard", "pradettes", "germaine_tillion", "zac_st-martin", "grand_selve", "jean_monnet", "lalande", "paleficat", "bourbaki", "alphand_meitner", "pastel", "quartier_pouvourville", "armand_duportal", "lapujade", "st-joseph", "soupetard", "montaudran_guillaumet", "quartier_gonin", "st_thomas_aquin", "fabre", "michoun", "lardenne", "etiennes_billieres", "jean_pierre_vernant", "emilie_rodat", "buffon", "viollet_duc", "alphand_meitner", "cuvier", "bourliaguet", "curie", "montaudran", "jean_dieuzaide", "e._rodat", "quartier_terrasse", "tbs", "soupetard_acacias_ariane", "saouzelong", "michelet", "lakanal", "peyroliere", "fermat", "jean_mace", "brassart", "pouvourville", "bonhoure", "soupetard_ariane", "guillaumet", "st_martin", "jean_zay", "stade_ernest_wallon", "fleurance", "duportal", "pierre_marie_curie", "impasse_butinon", "maurice_becanne", "leygue", "e._billieres", "balma_labege_argoulets", "henri_guillaumet", "sainte_therese", "saint-joseph", "lapujade", "anatole_france", "ramelet", "marengo-periole", "st_cyprien", "saint_cyprien", "fontaines_garonne", "faucher", "bordeblanche", "ancely", "arenes_romaines", "capitole", "cartoucherie", "vestrepain_fontaine_lestang_biscottes", "bois_limayrac", "carrefour_pierre_marie", "marcel_loubens", "izards-trois_cocus", "sept_deniers", "sept-deniers", "ernest_renan", "saint-simon","salade_ponsan", "jean_calas","silvio_trentin", "jean_rieux", "mac_clavel", "corraze", "toulouse-lautrec", "etienne_billieres", "borderouge", "balma_quint-fonsegrives", "quartiers_roseraie_amouroux_argoulets",  "reynerie", "toulouse", "toulousain", "toulousaine", "toulousains", "toulousaines")

additional_locations <- c(additional_locations1, additional_locations2, additional_locations3, additional_locations4)


freq.ngrams.locations <- rbind(freq.ngrams.locations, 
                              data.frame(
                                  Var1 = additional_locations, Freq = NA))




```

```{r}
freq.ngrams.locations$regex <- paste0(
  "(?:,|\\\\.|!|-|\\\\?|:|\\\\/|;|\\\\(|\\\\))?",
  gsub(
    "_",
    "\\\\s*(?:,|\\\\.|!|-|\\\\?|:|\\\\/|;|-|\\\\(|\\\\))?\\\\s*(?:de\\\\s+la|de\\\\s+l'?|de|du|des|à|a|aux|et|\\\\&|au|le|la|les|l'?|d'?|,|;)?\\\\s*",
    freq.ngrams.locations$Var1
  ),
  "(?:,|\\\\.|!|-|\\\\?|:|\\\\/|;|\\\\(|\\\\))?"
)

freq.ngrams.locations$key <- paste0("{{LOCATION_NAME_", row.names(freq.ngrams.locations), "}}")


for (i in seq_len(nrow(freq.ngrams.locations))) {
  #print(i)
  bp_toulouse$contenu_raw <- gsub(
    freq.ngrams.locations$regex[i],
    freq.ngrams.locations$key[i],
    bp_toulouse$contenu_raw,
    ignore.case = T,
    perl = T
  )
}


```

#### Build TF-IDF

```{r tf-idf}

dtm <- dfm(toulouse.compound.tokens)
docvars(dtm, "year") <- bp_toulouse$année
docvars(dtm, "category") <- bp_toulouse$nom.catégorie
docvars(dtm, "territory") <- bp_toulouse$nom.territoire
docvars(dtm, "project") <- bp_toulouse$nom_page_projets
docvars(dtm, "status") <- bp_toulouse$état



dtm <- dfm_trim(dtm, min_docfreq = 15)
dtm
```

## Step 7: Run STM (Toulouse only)

### Select k

#### Compute metrics

```{r}

k.cand <- seq(10, 250, 10)

for(k in k.cand){

  mod <- stm(
    documents = dtm,
    data = docvars(dtm),
    K = k,
    prevalence =~ status + year,
    max.em.its = 75,
    seed = 4023330,
    init.type = "Spectral",
    verbose = T
  )

  # metrics
  semcoh <- semanticCoherence(mod, dtm)
  exclus <- exclusivity(mod)

  df.temp <- data.frame(
    coherence = semcoh,
    exclusivity = exclus,
    k = k
  )

  df.plot.temp <- data.frame(
    coh = mean(df.temp$coherence),
    exc = mean(df.temp$exclusivity),
    lower.coh = min(df.temp$coherence),
    max.coh = max(df.temp$coherence),
    lower.ex = min(df.temp$exclusivity),
    max.ex = max(df.temp$exclusivity),
    k = k
  )

  if(k == min(k.cand)){
      df.plot <- df.plot.temp
    }
    else{
      df.plot <- rbind(df.plot, df.plot.temp)
    }

}

head(df.plot)

```

#### Plot metrics

```{r }

df.plot.long <- reshape2::melt(df.plot, id.vars = c('k'))
df.plot.long <- df.plot.long[df.plot.long$variable %in% c('coh', 'exc'),] # ignore upper/lower boundaries

ggplot(data = df.plot.long, aes(x = k, y = value, group = variable, color = variable)) +
  geom_line() +
  facet_wrap(.~variable, scale = 'free') +
  labs(y = '', title = 'Line Chart of exclusivity and coherence across K') +
  theme_bw() + 
  theme(legend.position="none")


```

#### Finding plateau

```{r plateau}

diff.exc <- abs(diff(df.plot$exc)) # get difference between 10 and 20, 20 and 30, and so on. 
diff.exclus.df <- as.data.frame(cbind(seq(10, 100, 10), diff.exc)) 

ggplot(diff.exclus.df, aes(V1, diff.exc)) +
  geom_line() +
  geom_point() +
  labs(x = "Number of Topics (K)",
       y = "Gain in Exclusivity",
       title = "Absolute Difference in Avg. Exclusivity",
       subtitle = "between K and K-10")

diff.coh <- abs(diff(df.plot$coh)) # get difference between 10 and 20, 20 and 30, and so on. 
diff.coh.df <- as.data.frame(cbind(seq(10, 100, 10), diff.coh)) 
ggplot(diff.coh.df, aes(V1, diff.coh)) +
  geom_line() +
  geom_point() +
  labs(x = "Number of Topics (K)",
       y = "Loss in Coherence",
       title = "Absolute Difference in Avg. Coherence",
       subtitle = "between K and K-10")


```

##### K-Robust

```{r}

fm <- vector()
k.cand <- seq(10, 100, 10)

start.time <- Sys.time()

for(k in 1:(length(k.cand)-1)){

  if(k == 1){
    
    mod <- stm(
      documents = dtm,
      data = docvars(dtm),
      K = k.cand[k],
      prevalence =~ status + year,
      max.em.its = 75,
      seed = 4023330,
      init.type = "Spectral",
      verbose = T
    )

    theta <- data.frame(mod$theta)
    theta$max <- apply(theta, 1, which.max)
  }

  # K+1 model
  k2 <- k + 1

  mod <- stm(
    documents = dtm,
    data = docvars(dtm),
    K = k.cand[k2],
    prevalence =~ status + year,
    max.em.its = 75,
    seed = 4023330,
    init.type = "Spectral",
    verbose = T
  )

  theta2 <- data.frame(mod$theta)
  theta2$max <- apply(theta2, 1, which.max)

  cat(k, k.cand[k], ncol(theta), "\n")
  cat(k2, k.cand[k2], ncol(theta2), "\n")

  fm[k] <- dendextend::FM_index_R(
    theta$max,
    theta2$max,
    assume_sorted_vectors = TRUE
  )

  # reuse K+1 as next K
  theta <- theta2
}


```

# Stuttgart

## Step 0 : Load the data

```{r load data}

bp_stuttgart <- read.csv(here("data", "propositions_stuttgart.csv"), sep = ",")
bp_stuttgart <- bp_stuttgart %>% 
  distinct(node.nr., .keep_all = TRUE) %>%
  filter(year %in% c(2021, 2023))
  

bp_stuttgart$status <- bp_stuttgart$status %in% c("umgesetzt", "wird umgesetzt", "wurde umgesetzt", "Gemeinderat hat teilweise zugestimmt", "Gemeinderat hat zugestimmt", "bereits teilweise umgesetzt")
```

## Step 2: Wrangling

### Erase all locations

```{r}

bp_stuttgart$contenu_raw <- bp_stuttgart$desc

matches <- read.csv(here("strassen_stgt.csv"), sep = ",")

matches$key <- paste0(" {{LOCATION_NAME_", as.numeric(row.names(matches)) + nrow(freq.ngrams.locations), "}} ")


for (i in seq_len(nrow(matches))) {
  #print(i)
  bp_stuttgart$contenu_raw <- gsub(
    trimws(matches$street[i]),
    matches$key[i],
    bp_stuttgart$contenu_raw,
    ignore.case = T,
    perl = T
  )
}


```

## Step 3: Translate text

```{r}
bp_stuttgart$contenu_raw_google_translated<- NA

for(i in seq_len(nrow(bp_stuttgart))) {
  print(i)
  bp_stuttgart$contenu_raw_google_translated[i] <-
    google_translate(
      bp_stuttgart$contenu_raw[i],
      target_language = "en",
      source_language = "de"
    )

}

write.csv(bp_stuttgart, "bpstuttgart_translation.csv")

```

# All

## Step 1: Combine the two datasets

```{r}
bp_stuttgart <- read.csv(here("bpstuttgart_translation.csv"), sep = ",")

colnames(bp_toulouse)
colnames(bp_stuttgart)

bp_toulouse$city <- "Toulouse"
bp_stuttgart$city <- "Stuttgart"


bp <- data.frame(
  content = c(bp_toulouse$contenu_raw_google_translated, bp_stuttgart$contenu_raw_google_translated),
  status = c(bp_toulouse$état, bp_stuttgart$status),
  city = c(bp_toulouse$city, bp_stuttgart$city),
  support = c(bp_toulouse$soutien + bp_toulouse$vote, bp_stuttgart$score_gut),
  response = c(paste0(bp_toulouse$reponse, " ", bp_toulouse$modalities), paste0(bp_stuttgart$ergebnis_haushaltsberatungen, " ", bp_stuttgart$stellungnahme_verwaltung, " ", bp_stuttgart$bezirksbeiratshinweis))
)

```

## Step 2: Tokenize translated text

```{r tokenize-en}


bp$content <- gsub("[\\.\\:\\?,!\\]", "",
                                     bp$content)

translated.toks <- tokens(bp$content,
                                   remove_symbols = T,
                                   remove_punct = T,
                                   remove_numbers = T,
                                   remove_separators = T
                              )
translated.toks <- tokens_select(translated.toks,
                              "location\\s*_\\s*name\\s*_\\s*[0-9]+",
                              selection = "remove",
                              valuetype = "regex")

translated.toks <- tokens_remove(tokens_tolower(translated.toks), stopwords("en"))


# lemmatise each word ONCE
translated.lemma_lookup <- setNames(
  textstem::lemmatize_strings(
    unique(
      tolower(
        unlist(
          as.list(translated.toks)
          )
        )
      )
    ), 
  unique(
    tolower(
      unlist(
        as.list(translated.toks)
        )
      )
    )
  )


# replace tokens via lookup
translated.lemmatised_list <- lapply(
    as.list(translated.toks), function(x) {
    translated.lemma_lookup[tolower(x)]
  }
)

translated.lemma.toks <- tokens(translated.lemmatised_list)


translated.tokens <- tokens_select(
    tokens(translated.lemmatised_list), 
    pattern = "^[0-9]+(\\.[0-9]+)?$", 
    selection = "remove", 
    valuetype = "regex"
  )


translated.toks.ngrams <- tokens_ngrams(translated.tokens, n= 2:3)


translated.toks.ngrams <- tokens_select(
  translated.toks.ngrams,
  pattern = "location_name_[0-9]+",
  selection = "remove",
  valuetype = "regex",
  case_insensitive = TRUE
)


translated.freq.ngrams <- as.data.frame(
  table(as.character(translated.toks.ngrams)), decreasing =T)


ngram.insert <- gsub("_", " ", 
    as.character(
      translated.freq.ngrams[order(
      -translated.freq.ngrams$Freq),][1:200,]$Var1))


compound.tokens <- tokens_compound(translated.tokens, phrase(ngram.insert), concatenator =  "_", join = F)


```

## Step 3: Build DTM

```{r tf-idf}

dtm <- dfm(compound.tokens)
docvars(dtm, "status") <- factor(bp$status)
docvars(dtm, "city") <- factor(bp$city)
docvars(dtm, "support") <- bp$support



dtm <- dfm_trim(dtm, min_docfreq = 10)
dtm <- dtm[ntoken(dtm) > 0, ]

dtm
```

## Step 4: Set k

#### Compute metrics

```{r}

dtm.stm <- convert(dtm, to = "stm")

k.cand <- seq(20, 85, 1)

k.out <- searchK(
  documents = dtm.stm$documents,
  vocab     = dtm.stm$vocab,
  K         = k.cand,
  prevalence = ~ status + city + support,  # your covariates from meta
  data      = dtm.stm$meta,
  emtol      = 0.000015,   # speeds up convergence
  verbose   = TRUE
)

# Plot the built-in diagnostics
plot(k.out)

k.out

median(c(
       which.max(k.out$results$semcoh),
       which.max(k.out$results$heldout),
       which.min(k.out$results$residual)
))

c(
  semcoh   = k.out$results$K[order(unlist(k.out$results$semcoh),   decreasing = TRUE)[1:10]],
  exclus   = k.out$results$K[order(unlist(k.out$results$exclus),   decreasing = TRUE)[1:10]],
  heldout  = k.out$results$K[order(unlist(k.out$results$heldout),  decreasing = TRUE)[1:10]],
  residual = k.out$results$K[order(unlist(k.out$results$residual), decreasing = FALSE)[1:10]]
)
```

#### Plot metrics

```{r }

df.plot.long <- reshape2::melt(df.plot, id.vars = c('k'))
df.plot.long <- df.plot.long[df.plot.long$variable %in% c('coh', 'exc'),] # ignore upper/lower boundaries

ggplot(data = df.plot.long, aes(x = k, y = value, group = variable, color = variable)) +
  geom_line() +
  facet_wrap(.~variable, scale = 'free') +
  labs(y = '', title = 'Line Chart of exclusivity and coherence across K') +
  theme_bw() + 
  theme(legend.position="none")


```



## Step 5: Run STM

```{r run-stm}

dtm <- dtm[ntoken(dtm) > 0, ]

poliblogPrevFit <- stm(
  documents = dtm, # input. can be a quanteda `dfm` or produced with stm's `prepdocuments`
  data = docvars(dtm), # provide the meta data
  K = 69, # number of topics chosen; we will discuss model choice in greater detail in the last session.
  prevalence =~   status + city + support , # attributes used as covariates (X_d)
  max.em.its = 100, # maximum number of iterations; here, after 75 iterations with no satisfying result, the stm stops
  seed = 4023330, # set seed; this specific seed is used to mirror results in vignette; only necessary if "spectral" is *not* used below
  init.type = "Spectral", # highly recommended. Provides consistent results based on the method of moments, which is deterministic and globally consistent. This means that no matter the seed that is set, the same results will be generated (with slight differences explained in footnote 10 of the vignette).
  verbose = T) # turns on/off  whether information should be printed to the screen



```

##### Analyse STM

```{r}

labelTopics(poliblogPrevFit)

```

##### Wordclouds

```{r wordclouds}

cloud(poliblogPrevFit, topic = 3, scale = c(2,.25))

```

##### Label topics

```{r}

l <- labelTopics(poliblogPrevFit, topics = 20, n = 10)
prob <- list()
frex <- list()
for(i in c(1:20)){
  prob[[i]] <- paste(l$prob[i,], collapse = ' ')
  frex[[i]] <- paste(l$frex[i,], collapse = ' ')
}
topic_labels <- data.frame(Prob = unlist(prob), Frex = unlist(frex), Topics = 1:20)
head(topic_labels)

```

```{r topic-prevalence}

plot(poliblogPrevFit, type = "summary", xlim = c(0, .3), n = 5)


```

##### Text / Covariates

```{r}

prep <- estimateEffect(1:69 ~ status + city + support, poliblogPrevFit, meta = docvars(dtm), uncertainty = "None") # using estimateeffect to get prevalences by groups; uncertainty provides CI, but is very time-intensive

prep$meta$status <- factor(prep$meta$status)
prep$meta$city <- factor(prep$meta$city)


plot(prep, covariate = "status",
     topics = c(1:69),
     model = poliblogPrevFit,
     method = "difference",
     cov.value1 = TRUE, 
     cov.value2 = FALSE,
     xlab = "More Accepted ... More Refused",
     main = "Effect of Accepted vs. Refused",
     xlim = c(-.1, .1), labeltype = "custom",
    )

plot(prep, covariate = "city",
     topics = c(1:69),
     model = poliblogPrevFit,
     method = "difference",
     cov.value1 = "Stuttgart", 
     cov.value2 = "Toulouse",
     xlab = "More Stuttgart ... More Toulouse",
     main = "Effect of Stuttgart vs. Toulouse",
     xlim = c(-.1, .1) ,  labeltype = "custom"  )
```

##### Perspectives

```{r perspectives}

meta.names <- c("état")

processed <- stm::textProcessor(
  bp_toulouse$contenu_raw_google_translated,
  metadata = bp_toulouse[, "état", drop = FALSE],
  stem = FALSE,
  lowercase = FALSE,
  removepunctuation = FALSE,
  removestopwords = FALSE,
  removenumbers = FALSE
)
names(processed)
# We omit all those default functions (`stem`, `lowercase`, etc.), because we have done that already or don't want to do it. 
out <- stm::prepDocuments(processed$documents, processed$vocab, processed$meta, lower.thresh = 15) # Default: lower.thresh=1 (words in only 1 doc will be dropped). 

poliblogContent <- stm(out$documents, out$vocab, K = 20, prevalence =~ état, content =~ état ,max.em.its = 75, data = out$meta, init.type = "Spectral")


plot(poliblogContent, type = "perspectives", topics = 5)


```

### Stuttgart
